### 2017-01-31 local-capability-machine.tex
addressed a couple of comments

        H^\sta(\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})(W)$ \dominique{apply to world?}:\\ This region matches only this memory segment.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,=,H^\pwl_{\start,\addrend}) \\
  \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Wor \monwknefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\}
\end{align*}
\lau{What is the reason to have the ``view'' always be $\temp$? It seems like it does not play well with the read condition if it is always $\temp$.}
\dominique{The comment immediately above is outdated, right?}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi_\pub,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

@@

  To this end let $b\not\in[\start,\addrend]$ and define the worlds:
  \begin{align*}
    \xi (W)  =& [0 \mapsto \iota^\pwl_{\start,\addrend}]  \\ 
              & [1 \mapsto \iota^\pwl_{b,b}] \\
    \xi (W')  =& [0 \mapsto \iota^\pwl_{\start,\addrend}]  \\ 
              & [1 \mapsto \revoked] 
  \end{align*}
  \dominique{The above still needs updating now that revoked regions remember
    what they used to look like.}
  For these two worlds, we have $\xi(W') \futurestr \xi(W)$ and from mono.\ of $\xi^{-1}$, we have $W' \futurestr W$. Now define the following memory segment:
  \[
    \ms = [\start \mapsto ((\readonly,\local),b,b,b), \start+1 \mapsto 0, \dots , \addrend \mapsto 0]
  \]
  It is the case that
  \[
    \npair{\ms} \in H \; 1 \; W
  \]
  but
  \[
    \npair{\ms} \not\in H \; 1 \; W'
  \]
  as it is not the case that \lau{what if $n=1$? Need to figure out when exactly this holds}
  \[
    \npair[n-1]{((\readonly,\local),b,b,b)} \in \stdvr(\xi(W')).
  \]
  The only other option that remains is $v=\temp$.
\end{proof}
\lau{$a \leq b$ that the interpretation is not empty.}

>>>>

        H^\sta(\ms_\stk'|_{[\start_\stk,\start_\stk''-1]})(1)(W)$ :\\ This region matches only this memory segment.

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota_{\start,\addrend}^\pwl : \Regions\\
  &\iota_{\start,\addrend}^\pwl \defeq (\temp,1,=,=,H^\pwl_{\start,\addrend}) \\
  \\
  &H^\pwl : \Addrs^2 \fun \States \fun (\Wor \monwknefun \UPred{\HeapSegments})\\
  &H^\pwl_{\start,\addrend}\; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = [\start,\addrend] \land \\
      &\forall \addr \in [\start,\addrend] \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi_\pub,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
\newcommand{\wrev}[1]{\revokeTemp{#1}}

@@

  To this end let $b\not\in[\start,\addrend]$ and define the worlds:
  \begin{align*}
    \xi (W)  =& [0 \mapsto \iota^\pwl_{\start,\addrend}]  \\ 
              & [1 \mapsto \iota^\pwl_{b,b}] \\
    \xi (W')  =& [0 \mapsto \iota^\pwl_{\start,\addrend}]  \\ 
              & [1 \mapsto \revoked] 
  \end{align*}
  For these two worlds, we have $\xi(W') \futurestr \xi(W)$ and from mono.\ of $\xi^{-1}$, we have $W' \futurestr W$. Now define the following memory segment:
  \[
    \ms = [\start \mapsto ((\readonly,\local),b,b,b), \start+1 \mapsto 0, \dots , \addrend \mapsto 0]
  \]
  It is the case that
  \[
    \npair{\ms} \in H \; 1 \; W
  \]
  but
  \[
    \npair{\ms} \not\in H \; 1 \; W'
  \]
  as it is not the case that \lau{what if $n=1$? Need to figure out when exactly this holds}
  \[
    \npair[n-1]{((\readonly,\local),b,b,b)} \in \stdvr(\xi(W')).
  \]
  The only other option that remains is $v=\temp$.
\end{proof}
\lau{$a \leq b$ that the interpretation is not empty.}
